%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Samson Olusegun} \\[7.5pt]
\textbf{Software Engineer} \\[10pt]
\normalsize{\textit{Experience Summary}: A results-driven Software Engineer with a proven track record in translating business needs into efficient technical solutions. Specializes in Typescript, Rust, Python, and Cloud Development, with a keen interest in database systems. Committed to continuous learning and innovation, actively engaged in both tech and non-tech communities. Passionate about mentoring and fostering growth within these networks.} \\[10pt]
\href{https://linkedin.com/in/samson-olusegun}{\raisebox{-0.05\height}\faLinkedin\ Samson-Olusegun} \  $|$ \
\href{https://twitter.com/nully0x}{\raisebox{-0.05\height}\faTwitter\ nully0x} \ $|$ \  
\href{https://github.com/nully0x}{\raisebox{-0.05\height}\faGithub\ nully0x} \ $|$ \
\href{https://www.nully0x.xyz}{\raisebox{-0.05\height}\faGlobe\ nully0x.xyz} \ $|$ \
\href{mailto:nully0x@proton.me}{\raisebox{-0.05\height}\faEnvelope\ nully0x@proton.me} \ $|$ \
\href{tel:+2349160918616}{\raisebox{-0.05\height}\faMobile\ +2349160918616}
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

\section{TECHNICAL EXPERIENCE}

\begin{joblong}{ChainCode Labs, US -- Open Source Developer(Remote)}{March 2023 -- Present}
\item Streamlined data pipeline development for ChatBTC, enhancing knowledge base app performance.
\item Engineered a robust backend system for a review feature in knowledge-based applications, improving user engagement.
\item Designed and implemented a cost-effective deployment pipeline, ensuring high availability and reliability.
\item Spearheaded the integration of the lightning network for sat rewards and L402 payment requests, boosting transaction efficiency.
\end{joblong}

\begin{joblong}{Propel, Germany -- Technical Jury(Remote)}{November 2022 -- January 2024}
\item Led technical assessments, achieving a 15\% increase in candidate selection accuracy against predefined criteria.
\item Established and enforced evaluation criteria, streamlining the hiring process by 20\%.
\item Facilitated collaboration among jury members and hiring managers, reducing review times by 25\%.
\item Ensured compliance with data protection standards through meticulous record keeping of candidate assessments and feedback.
\end{joblong}

\begin{joblong}{BitPayRoll, Abuja -- Technical Team Lead (Remote-Part Time)}{October 2022 -- Present}
\item Guided the design team in developing a user journey framework, enhancing user experience.
\item Built scalable backend services leveraging the bitcoin protocol, supporting innovative financial solutions.
\item Engineered a deployment pipeline, optimizing resource allocation and operational efficiency.
\end{joblong}

\begin{joblong}{Helgg, Lagos -- Lead Backend Engineer (Remote-Part Time)}{August 2022 -- May 2023}
\item Architected backend systems for e-scooter mobility and monitoring, driving technological advancements in urban transportation.
\item Championed technical excellence and best practices in backend engineering, setting new benchmarks for quality and efficiency.
\item Designed systems with foresight, addressing operational challenges proactively and effectively.
\end{joblong}

\begin{joblong}{Qala Dev, Lagos -- Bitcoin Protocol Developer Intern (Remote)}{January 2021 -- July 2021}
\item Immersed in the study of the Bitcoin protocol, gaining deep insights into blockchain technology.
\item Engaged in discussions on the Bitcoin and Lightning Network protocols, contributing to project implementations.
\item Contributed to open-source projects, enhancing community knowledge and fostering innovation in cryptocurrency technologies.
\end{joblong}

\begin{joblong}{Adekunle Ajasin University, Ondo -- Web Developer}{January 2021 -- June 2021}
\item Developed and deployed web applications for student portal management, utilizing AdonisJs and Heroku.
\item Collaborated closely with the lead web developer, ensuring rigorous testing and quality assurance of web applications.
\item Diagnosed and resolved web application errors, minimizing downtime and enhancing user satisfaction.
\end{joblong}

\section{OTHER EXPERIENCE}

\begin{joblong}{Tech4Dev, Lagos -- Frontend Development Consultant (Contract)}{August 2022 -- June 2023}
\item Curated and delivered comprehensive coursework for Frontend Engineering, aligning with industry standards.
\item Provided essential materials and resources to trainees, facilitating their successful completion of the training program.
\item Designed and administered periodic assessments, evaluating trainee progress and understanding.
\item Fostered a culture of continuous learning and curiosity among trainees, encouraging lifelong engagement with technology.
\end{joblong}


\section{EDUCATION}

\begin{tabularx}{\linewidth}{@{}l X@{}}
Adekunle Ajasin University & \textbf{Bachelor of Science in Economics} \\
                          & December 2015 - April 2021 \\[10pt]
\end{tabularx}

\section{SKILLS}

\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Programming} & HTML / CSS / Javascript Typescript / Python / Rust / Bitcoin Script / Zig \\
\textbf{Concepts} & Design Implementation / Test-Driven Development / Microservices / Monolithics \\
\textbf{Web Frameworks} & Angular / NodeJs / AdonisJs / Express / Actix / Svelte / Axum \\
\textbf{Database} & MySQL / Firestore / MongoDB / PostgreSQL / DynamoDB \\
\textbf{Tools} & Github Actions / Git / PowerApps / Docker / TravisCI / Kubernetes /  \\
\textbf{Data Processing} & Google Colab / Google Data Lab / Azure Data Studio / Microsoft Power BI / Eviews / SPSS / Excel \\
\textbf{Cloud} & Google Cloud Platform / Azure / AWS / Heroku / Oracle Cloud
\end{tabularx}

\section{INTEREST}
Data / Bitcoin / Movies / Traveling

\section{LANGUAGES}
English / Yoruba / French (Beginner)

\section{PROJECTS}

\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Serverless Veeds} & \hfill \href{https://github.com/nully0x/serverless-veeds}{Github} \\
& Developed to illustrate video sharing using serverless architecture within GCP ecosystem\\[10pt]
\textbf{Tweet Annotator Helpers} & \hfill \href{https://github-gist.com}{github-gist} \\
& Developed to annotate and classify text (tweets) extracts using Twitter API, to further subject to sentiment analysis. \\[10pt]
\textbf{Udagram} & \hfill \href{https://github.com}{github} \\
& An image-sharing web app. Implementing a set of resources on the AWS cloud environment using various stacks such as Kubernetes, RDS, S3, Cloudformation, Amplify, Docker, Nodejs and Ionic/Angular
\end{tabularx}

\section{CERTIFICATE}
\textbf{Cloud Developer Nanodegree} - Udacity

\vfill
\center{\footnotesize Last updated: \today}

\end{document}